\noindent In this lab, you will use a two-stage melting model to extract the continental and oceanic crust from Earth's primitive mantle.

\medskip

\noindent The model begins with the \emph{primitive mantle} (Lab 2): a geochemical estimate of the mantle composition immediately after core formation, before any crust was extracted. Equivalently, it is the composition you would obtain by mixing the entire crust back into the present-day mantle. You will model Earth's differentiation in two discrete stages of melt extraction:

\begin{itemize}
	\item Stage 1: A partial melt of the \emph{primitive mantle} is extracted to form the continental crust, leaving behind a mantle depleted in highly incompatible elements.
	\item Stage 2: A partial melt of the resulting \emph{depleted mantle} is extracted to form the oceanic crust.
\end{itemize}

\noindent You will use \textbf{fractional melting} equations to model each stage, and you will compare your modeled melts to the average composition of continental crust and mid-ocean ridge basalt (oceanic crust).


\medskip
\noindent The \textbf{partition coefficient}, $D$, describes the ratio of concentrations for an element between a mineral and a melt at equilibrium:

$$D=\frac{C_S}{C_L}$$

\noindent \textbf{Fractional melting} describes a scenario where some fraction of a rock melts and that melt is immediately separated from the rock. The concentration of a trace element in the remaining rock is described by this equation:

$$\frac{C_S}{C_0}=\left(1-F\right)^{^{\left(\tfrac{1}{D}-1\right)}}$$

\noindent The concentration of a trace element in an infinitely small fraction of melt, often referred to as the \emph{instantaneous melt}, is described by this equation:

$$\frac{C_L}{C_0}= \frac{\left(1-F\right)^{^{\left(\tfrac{1}{D}-1\right)}}}{D}$$

\noindent C is the concentration of a trace element. Subscript L represents the melt phase. Subscript S represents the solid phase. C$_0$ means at the initial conditions when solid is 100\% of the system. D is the partition coefficient, and F is the melt fraction (where 1 is 100\% melt).
